Models

### 2024-05-14 analysis/05_model_metrics.Rmd
Fix the duration models

study_time_data <- model_data %>% 
  dplyr::select(study_id, startyear, duration) %>% 
  distinct() %>%
  group_by(study_id) %>%
  filter(startyear == min(startyear))

study_slope_data <- indv_mod_table %>%
  filter(term == "year_scaled") %>%
  dplyr::select(study_id, metric, estimate) %>%
  left_join(meta %>% 
              mutate(study_id = as.character(study_id))) %>%
  left_join(model_data %>% dplyr::select(study_id, startyear, duration) %>% distinct())

>>>>

study_time_data <- model_data %>% 
  dplyr::select(study_id, startyear, duration) %>% 
  distinct() %>%
  group_by(study_id) %>%
  mutate(startyear = min(startyear), duration = max(duration)) %>%
  distinct()

study_slope_data <- model_output %>%
  filter(!is.na(study_id), term == "year_scaled") %>%
  dplyr::select(study_id, metric, estimate) %>%
  left_join(study_time_data)
